---
title: "Useful Plants of Amazonia 1.0a1"
# author: "Nisha Marwaha"
# date: "`r Sys.Date()`"
# output: html_document
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: default
    source_code: "https://github.com/nmarwaha/useful-plants-of-amazonia/tree/gh-page"
  # html_document: # not clear what this does
  #   self_contained: false # not clear what this does
runtime: shiny
---

<style>
.dropdown-menu > li > a:hover,
.dropdown-menu > li > a:focus {
  text-decoration: none;
  color: #ffffff;
  background-color: #355e3b;
}
.dropdown-menu > .active > a,
.dropdown-menu > .active > a:hover,
.dropdown-menu > .active > a:focus {
  color: #ffffff;
  text-decoration: none;
  outline: 0;
  background-color: #355e3b;
}

.nav .open > a,
.nav .open > a:hover,
.nav .open > a:focus {
  background-color: #e6e6e6;
  border-color: #355e3b;
}

.nav-pills > li.active > a,
.nav-pills > li.active > a:hover,
.nav-pills > li.active > a:focus {
  color: #ffffff;
  background-color: #355e3b;
}

.navbar-inverse {
  background-color: #355e3b;
  border-color: #014421;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
  color: #ffffff;
  background-color: #014421;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: #ffffff;
  background-color: #014421;
}

.navbar-inverse .navbar-toggle:hover,
.navbar-inverse .navbar-toggle:focus {
  background-color: #014421;
}

.navbar-inverse .navbar-collapse,
.navbar-inverse .navbar-form {
  border-color: #013220;
}
.navbar-inverse .navbar-nav > .open > a,
.navbar-inverse .navbar-nav > .open > a:hover,
.navbar-inverse .navbar-nav > .open > a:focus {
  background-color: #014421;
  color: #ffffff;
}
@media (max-width: 767px) {
  .navbar-inverse .navbar-nav .open .dropdown-menu > .dropdown-header {
    border-color: #014421;
  }
  .navbar-inverse .navbar-nav .open .dropdown-menu .divider {
    background-color: #014421;
  }

  .navbar-inverse .navbar-nav .open .dropdown-menu > li > a:hover,
  .navbar-inverse .navbar-nav .open .dropdown-menu > li > a:focus {
    color: #ffffff;
    background-color: #014421;
  }
  .navbar-inverse .navbar-nav .open .dropdown-menu > .active > a,
  .navbar-inverse .navbar-nav .open .dropdown-menu > .active > a:hover,
  .navbar-inverse .navbar-nav .open .dropdown-menu > .active > a:focus {
    color: #ffffff;
    background-color: #014421;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(sf)
library(purrr)
library(leaflet)
library(leaflet.extras)
library(htmlwidgets)
library(htmltools)
library(shiny)
library(shinyWidgets)
library(dplyr)
library(tidyverse)

# setwd("~/Documents/GitHub/useful-plants-of-amazonia")
```

All Data {data-navmenu="Database Maps"}
===================================== 
Column
-----------------------------------------------------------------------
###

```{r map data}
# load database
DB_raw <- read.csv("camara_powo_vpa_new_rclverified_website.csv", encoding = "UTF-8") # accented characters not yet displayed, check source file; should add guess_max = Inf for good practice
DB_raw_languages <- DB_raw[!(is.na(DB_raw$glotto_lat) | DB_raw$glotto_lat=="" | is.na(DB_raw$glotto_lon) | DB_raw$glotto_lon==""), ]
amazonia <- read_sf('Lim_Biogeografico.shp') %>%
  st_transform('+proj=longlat +datum=WGS84')

# set map view parameters
initial_lat <- mean(range(as.numeric(DB_raw_languages$glotto_lat), na.rm = TRUE)) # -4.63, at time of testing with DBv1
initial_lng <- mean(range(as.numeric(DB_raw_languages$glotto_lon), na.rm = TRUE)) # -57.68
initial_zm <- 5
max_lat <- max(as.numeric(DB_raw_languages$glotto_lat), na.rm = TRUE) # 7.51
min_lat <- min(as.numeric(DB_raw_languages$glotto_lat), na.rm = TRUE) # -16.77
max_lng <- max(as.numeric(DB_raw_languages$glotto_lon), na.rm = TRUE) # -37.02
min_lng <- min(as.numeric(DB_raw_languages$glotto_lon), na.rm = TRUE) # -78.34

# aggregate rows with shared coordinates
DB_grouped <- DB_raw_languages %>%
  group_by(glotto_lat, glotto_lon) %>%
  summarise(
    tribe_lang_grouped = paste(unique(tribe_language), collapse = "; "),
    reference_grouped = paste("- ", unique(reference), collapse = "<br>"),
    popup_content = paste0(
      map_chr(sort(unique(species_resolved)), function(sp) {
        entries <- which(species_resolved == sp)  # for each species at this location
        sp_df <- data.frame(  # for those entries, group by use and subuse
          use_category = use_category_resolved[entries],
          use_subcategory = use_subcategory_resolved[entries],
          part = plant_part_resolved[entries],
          stringsAsFactors = FALSE
        )
        use_groups <- sp_df %>%  # need to sort alphabetically, would be better to organize subcategories under use categories
          group_by(use_category, use_subcategory) %>%
          summarise(parts = paste(unique(part), collapse = ", "), .groups = "drop")
        uses_parts <- paste0(
          purrr::pmap_chr(use_groups, function(use_category, use_subcategory, parts) {
            paste0(
              "<b>Use: </b>", use_category, ", ", use_subcategory, "<br><b>Part: </b>", parts
            )
          }),
          collapse = "<br>"
        )
        paste0(
          "<b><i>", sp, "</i></b><br>",  # to only show details after clicking species name use "<details><summary><b><i>", sp, "</i></b></summary>",
          uses_parts,
          "<br><br>"  # and "</details><br>"
        )
      }),
      collapse = ""
    ),
    .groups = "drop"
  )

DB_grouped$popup_content <- paste0(DB_grouped$popup_content,"<br><b>References</b><br>",DB_grouped$reference_grouped)
DB_grouped$id <- seq_len(nrow(DB_grouped)) # or use glottocode if better

# DB_grouped <- DB_grouped[1:10,] # to be removed after testing
```

```{r map UI setup}
# set up popup sidebar
tags$div(
  id = "popupSidebar",
  style = "
    position: fixed;
    top: 60px; right: 0;
    width: 30%;
    height: 90.85%;
    overflow-y: auto;
    background: white;
    border-left: 1px solid #ccc;
    padding: 15px;
    z-index: 1000;
    display: none;
  ",
  tags$div(
    style = "
      position: sticky;
      top: 0;
      background: none;
      padding: 5px 0;
      z-index: 1001;
    ",
    tags$button(
      "×",
      style = "
        background: white;
        border: none;
        font-size: 20px;
        cursor: pointer;
        float: right;
        margin-right: 10px;
      ",
      onclick = "document.getElementById('popupSidebar').style.display='none';"
      )
    ),
  tags$div(id = "popupContent", style = "margin-top: 10px;"),
# store popup content separately
  tags$div(id = "allPopups", style = "display:none;",
           lapply(1:nrow(DB_grouped), function(i) {
             tags$div(
               id = paste0("popup_", DB_grouped$id[i]),
               HTML(DB_grouped$popup_content[i])
               )
             })
           )
,
# load sidebar content by id
tags$script(HTML("
  function showSidebarById(id) {
    var content = document.getElementById('popup_' + id).innerHTML;
    document.getElementById('popupContent').innerHTML = content;
    document.getElementById('popupSidebar').style.display = 'block';
  }
"))
)
```

```{r map}
# map setup
DBmap <- leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
  addTiles() %>%  # add default OpenStreetMap map tiles
  setView(lat = initial_lat, lng = initial_lng, zoom = initial_zm) %>%
  setMaxBounds(
    lng1 = min_lng, lat1 = min_lat, # southwest corner
    lng2 = max_lng,  lat2 = max_lat # northeast corner
  ) %>%
  addPolygons(data = st_zm(amazonia), color = "#014421", weight = 5, opacity = 0.5, fill = FALSE, smoothFactor = 1) %>%
  addMarkers(lng=as.numeric(DB_grouped$glotto_lon), lat=as.numeric(DB_grouped$glotto_lat),
             popup = paste0(
               "<b>Language:</b> ", DB_grouped$tribe_lang_grouped, "<br>",
               "<button onclick=\"showSidebarById(",
               DB_grouped$id, 
               ")\" style='margin-top:5px; background-color:#007bff; color:white; border:none; padding:5px 10px; border-radius:4px; cursor:pointer;'>See more</button>"
               )
             ) %>%
  addEasyButton(easyButton(
    icon = "fa-search-plus", title = "Zoom in",
    onClick = JS("function(btn, map){ map.zoomIn(); }")
    )
  ) %>%
  addEasyButton(easyButton(
    icon="fa-home", title="Reset view",
    onClick = JS(sprintf("function(btn, map){ map.setView([%s, %s], %s); }", initial_lat, initial_lng, initial_zm))
    )
  ) %>%
  addEasyButton(  # need to ensure accented characters are properly encoded
    easyButton(icon = "fa-download", title = "Download data",
      onClick = JS("
        function(btn, map) {
          var link = document.createElement('a');
          link.href = 'camara_powo_vpa_new_rclverified_website.csv';
          link.download = 'useful-plants-of-amazonia.csv';
          document.body.appendChild(link);
          link.click();
          document.body.removeChild(link);
        }")
      )
    )

# print map
DBmap
```

Filter Data {data-navmenu="Database Maps"}
===================================== 
Column
-----------------------------------------------------------------------
###

```{r interactive map UI setup}
# DB_raw_languages <- DB_raw_languages[1:25,] # to be removed after testing

# set up map filter boxes
tags$div(
  style = "display: flex; gap: 10px; align-items: center; padding: 5px; border-radius: 8px; flex-wrap: wrap;", # background-color: #f8f9fa; box-shadow: 0 1px 3px rgba(0,0,0,0.1)
  div(
    style = "flex: 1;",
    pickerInput("species", "Species",
                choices = unique(DB_raw_languages$species_resolved),
                selected = unique(DB_raw_languages$species_resolved),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 1;",
    pickerInput("use", "Use",
                choices = unique(DB_raw_languages$use_category_resolved),
                selected = unique(DB_raw_languages$use_category_resolved),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 1;",
    pickerInput("part", "Plant part",
                choices = unique(DB_raw_languages$plant_part_resolved),
                selected = unique(DB_raw_languages$plant_part_resolved),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 1;",
    pickerInput("language", "Language",
                choices = unique(DB_raw_languages$tribe_language),
                selected = unique(DB_raw_languages$tribe_language),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 0; margin-top: 12px;",
    downloadButton("downloadData", "Data")),
# set up interactive map box
  div(
    style = "width: 100%; height: 650px; position: relative; margin-top: 10px;",
    leafletOutput("mymap", height = "100%")
    )
)
```

```{r interactive map}
# reactive data filtering
filtered_data <- reactive({
  # req(input$species, input$part, input$use, input$language)
  DB_raw_languages %>%
    filter(
      species_resolved %in% input$species,
      use_category_resolved %in% input$use,
      plant_part_resolved %in% input$part,
      tribe_language %in% input$language
    )
})

# initial map render
output$mymap <- renderLeaflet({
  leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
    addTiles() %>%
    setView(lat = initial_lat, lng = initial_lng, zoom = initial_zm) %>%
    # setMaxBounds(
    #   lng1 = min_lng, lat1 = min_lat, # southwest corner
    #   lng2 = max_lng,  lat2 = max_lat # northeast corner
    # ) %>%
  addPolygons(data = st_zm(amazonia), color = "#014421", weight = 5, opacity = 0.5, fill = FALSE, smoothFactor = 1) %>%
  addEasyButton(easyButton(
    icon = "fa-search-plus", title = "Zoom in",
    onClick = JS("function(btn, map){ map.zoomIn(); }")
    )
  ) %>%
  addEasyButton(easyButton(
    icon="fa-home", title="Reset view",
    onClick = JS(sprintf("function(btn, map){ map.setView([%s, %s], %s); }", initial_lat, initial_lng, initial_zm))
    )
  )
})

# update map markers dynamically
observe({
  leafletProxy("mymap", data = filtered_data()) %>%
    clearMarkers() %>%
    addMarkers(~as.numeric(glotto_lon), ~as.numeric(glotto_lat),
               popup = paste0("<b>Language:</b> ", ifelse(DB_grouped$tribe_lang_grouped != "", DB_grouped$tribe_lang_grouped, "N/A"), "<br>",
                    "<details style='margin-top:5px;'>", "<summary style='cursor:pointer; color:#007bff;'>See more</summary>",
                    "<br>", DB_grouped$popup_content)
              )
})

# dynamic download button
# need to ensure accented characters are properly encoded
output$downloadData <- downloadHandler(
  filename = function() {
    paste("useful-plants-of-amazonia-filtered-", Sys.Date(), ".csv", sep = "")
  },
  content = function(file) {
    write.csv(filtered_data(), file, row.names = FALSE)
  }
)
```

Home
===================================== 
Column {.tabset}
-----------------------------------------------------------------------
### ABOUT (`r Sys.Date()`)

The Useful Plants of Amazonia project is developed at Dr. Rodrigo Cámara-Leret's lab (https://rcamaraleret.com/), a research group focused on the conservation of biological and cultural heritage, in collaboration with Dr. Jordi Bascompte and Dr. Patrick R. Roehrdanz. It is supported by grants from the Swiss National Science Foundation, the National Science Foundation, and the Arnhold UC Santa Barbara-Conservation International Climate Solutions Collaborative. This website () was developed by Nisha Marwaha (https://github.com/nmarwaha).</br></br>

<b>Resources</b>

XX paper citation</br>
XX database citation</br>
XX github link</br>

<b>Data Downloads</b>

- You can use this dataset freely and share it with your collaborators.

- The data have been compiled either from the literature or fieldwork done by us or our collaborators. Data was incorporated from the original publications, unless it was requested from the original authors.

- Useful Plants of Amazonia () is not the author/owner of the data. It is only a way of sharing them with the community. If you decide to use this dataset, you must mention this web service: "This work used the Useful Plants of Amazonia database ()." This does not preclude citing the author of individual studies when needed. All references are located in the dataset file.

- Use this dataset at your own risk. We are not responsible for the accuracy of the results derived from your research.

- If you have any problems downloading the data, please let us know.

<b>How To Contribute</b>

- If you have a study that you think could be included in the database, please send us an e-mail. We are also happy to hear about any potential mistakes or other feedback.</br></br>

<b>Contact Information</b>

Rodrigo Cámara-Leret</br>
Department of Systematic and Evolutionary Botany</br>
University of Zurich</br>
Zollikerstrasse 107, 8008 Zurich</br>
Switzerland</br>
Phone: +41 (0)44 634 84 11</br>
E-mail: rodrigo.camaraleret@uzh.ch

```{r}

```

### ACERCA DE (`r Sys.Date()`)

El proyecto Plantas Útiles de la Amazonia se desarrolla en el laboratorio del Dr. Rodrigo Cámara-Leret (https://rcamaraleret.com/), un grupo de investigación centrado en la conservación del patrimonio biológico y cultural, en colaboración con el Dr. Jordi Bascompte y el Dr. Patrick R. Roehrdanz. Cuenta con el apoyo de becas de la Fundación Nacional Suiza para la Ciencia, la Fundación Nacional para la Ciencia y el Arnhold UC Santa Barbara-Conservation International Climate Solutions Collaborative. Este sitio web () fue desarrollado por Nisha Marwaha (https://github.com/nmarwaha).</br></br>

<b>Recursos</b>

XX cita del artículo</br>
XX cita de la base de datos</br>
XX enlace de Github</br>

<b>Descargas de Datos</b>

- Puede usar este conjunto de datos libremente y compartirlo con sus colaboradores.

- Los datos se han recopilado a partir de la literatura o del trabajo de campo realizado por nosotros o nuestros colaboradores. Los datos se incorporaron de las publicaciones originales, a menos que se solicitara a los autores originales.

- Plantas Útiles de la Amazonia () no es el autor ni el propietario de los datos. Es solo una forma de compartirlos con la comunidad. Si decide utilizar este conjunto de datos, debe mencionar este servicio web: "Este trabajo utilizó la base de datos Plantas Útiles de la Amazonia ()." Esto no impide citar al autor de estudios individuales cuando sea necesario. Todas las referencias se encuentran en el archivo del conjunto de datos.

- Utilice este conjunto de datos bajo su propia responsabilidad. No nos responsabilizamos de la exactitud de los resultados derivados de su investigación.

- Si tiene algún problema para descargar los datos, por favor, infórmenos.

<b>Cómo Contribuir</b>

- Si tiene un estudio que cree que podría incluirse en la base de datos, envíenos un correo electrónico. Nos complacerá recibir información sobre posibles errores u otros comentarios.</br></br>

<b>Información de Contacto</b>

Rodrigo Cámara-Leret</br>
Departamento de Botánica Sistemática y Evolutiva</br>
Universidad de Zúrich</br>
Zollikerstrasse 107, 8008 Zúrich</br>
Suiza</br>
Teléfono: +41 (0)44 634 84 11</br>
Correo electrónico: rodrigo.camaraleret@uzh.ch

### SOBRE (`r Sys.Date()`)

O projeto Plantas Úteis da Amazônia é desenvolvido no laboratório do Dr. Rodrigo Cámara-Leret (https://rcamaraleret.com/), um grupo de pesquisa focado na conservação do patrimônio biológico e cultural, em colaboração com o Dr. Jordi Bascompte e o Dr. Patrick R. Roehrdanz. É apoiado por bolsas da Fundação Nacional de Ciências da Suíça, da Fundação Nacional de Ciências e da Colaboração para Soluções Climáticas Arnhold UC Santa Barbara-Conservation International. Este site () foi desenvolvido por Nisha Marwaha (https://github.com/nmarwaha).</br></br>

<b>Recursos</b>

Citação do artigo XX</br>
Citação do banco de dados XX</br>
Link do GitHub XX</br>

<b>Downloads de Dados</b>

- Você pode usar este conjunto de dados livremente e compartilhá-lo com seus colaboradores.

- Os dados foram compilados a partir da literatura ou de trabalho de campo realizado por nós ou por nossos colaboradores. Os dados foram incorporados das publicações originais, a menos que solicitados aos autores originais.

- Plantas Úteis da Amazônia () não é o autor/proprietário dos dados. É apenas uma forma de compartilhá-los com a comunidade. Se você decidir usar este conjunto de dados, deverá mencionar este serviço web: "Este trabalho utilizou o banco de dados Plantas Úteis da Amazônia ()." Isso não impede a citação do autor de estudos individuais, quando necessário. Todas as referências estão localizadas no arquivo do conjunto de dados.

- Use este conjunto de dados por sua conta e risco. Não nos responsabilizamos pela precisão dos resultados derivados de sua pesquisa.

- Se tiver algum problema para baixar os dados, por favor, nos avise.

<b>Como Contribuir</b>

- Se você tiver um estudo que acha que poderia ser incluído no banco de dados, envie-nos um e-mail. Também ficaremos felizes em receber notícias sobre possíveis erros ou outros comentários.</br></br>

<b>Informações de Contato</b>

Rodrigo Cámara-Leret</br>
Departamento de Botânica Sistemática e Evolutiva</br>
Universidade de Zurique</br>
Zollikerstrasse 107, 8008 Zurique</br>
Suíça</br>
Telefone: +41 (0)44 634 84 11</br>
E-mail: rodrigo.camaraleret@uzh.ch

### À PROPOS (`r Sys.Date()`)

Le projet Plantes utiles d'Amazonie est développé au laboratoire du Dr Rodrigo Cámara-Leret (https://rcamaraleret.com/), un groupe de recherche axé sur la conservation du patrimoine biologique et culturel, en collaboration avec les Drs Jordi Bascompte et Patrick R. Roehrdanz. Il est soutenu par des subventions du Fonds national suisse de la recherche scientifique, de la Fondation nationale suisse de la recherche scientifique et du Arnhold UC Santa Barbara-Conservation International Climate Solutions Collaborative. Ce site web () a été développé par Nisha Marwaha (https://github.com/nmarwaha).</br></br>

<b>Ressources</b>

XX citation d'article</br>
XX citation de base de données</br>
XX lien GitHub</br>

<b>Téléchargements de Données</b>

- Vous pouvez utiliser cet ensemble de données librement et le partager avec vos collaborateurs.

- Les données ont été compilées à partir de la littérature ou de travaux de terrain réalisés par nous-mêmes ou nos collaborateurs. Les données ont été incorporées à partir des publications originales, sauf demande contraire des auteurs.

- Useful Plants of Amazonia () n'est ni l'auteur ni le propriétaire des données. Il s'agit simplement d'un moyen de les partager avec la communauté. Si vous décidez d'utiliser cet ensemble de données, vous devez mentionner ce service web: «Ce travail a utilisé la base de données Useful Plants of Amazonia ().» Cela n'empêche pas de citer l'auteur des études individuelles si nécessaire. Toutes les références se trouvent dans le fichier de l'ensemble de données.

- Utilisez cet ensemble de données à vos propres risques. Nous ne sommes pas responsables de l'exactitude des résultats issus de vos recherches.

- Si vous rencontrez des difficultés pour télécharger les données, n'hésitez pas à nous en informer.

<b>Comment Contribuer</b>

- Si vous pensez qu'une étude pourrait être incluse dans la base de données, veuillez nous envoyer un courriel. Nous serions également ravis de recevoir d'éventuelles erreurs ou commentaires.</br></br>

<b>Coordonnées</b>

Rodrigo Cámara-Leret</br>
Département de Botanique Systématique et Évolutive</br>
Université de Zurich</br>
Zollikerstrasse 107, 8008 Zurich</br>
Suisse</br>
Téléphone: +41 (0)44 634 84 11</br>
Courriel: rodrigo.camaraleret@uzh.ch

```{r}

```
