---
title: "Useful Plants of Amazonia"
# author: "Nisha Marwaha"
# date: "`r Sys.Date()`"
# output: html_document
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: default
    source_code: "https://github.com/nmarwaha/useful-plants-of-amazonia/tree/gh-page"
  # html_document: # not clear what this does
  #   self_contained: false # not clear what this does
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(flexdashboard)
library(leaflet)
library(leaflet.extras)
library(htmlwidgets)
library(shiny)
library(shinyWidgets)
library(dplyr)

# setwd("~/Documents/GitHub/useful-plants-of-amazonia")
```

All Data {data-navmenu="Database Maps"}
===================================== 
Column
-----------------------------------------------------------------------
###

```{r map setup}
# load database
DB_raw <- read.csv("camara_powo_vpa_new_rclverified_website.csv", encoding = "UTF-8") # accented characters still not displayed; should add guess_max = Inf for good practice

# set map view parameters
initial_lat <- mean(range(as.numeric(DB_raw$glotto_lat), na.rm = TRUE)) # -4.63, at time of testing with v1
initial_lng <- mean(range(as.numeric(DB_raw$glotto_lon), na.rm = TRUE)) # -57.68
initial_zm <- 5
max_lat <- max(as.numeric(DB_raw$glotto_lat), na.rm = TRUE) # 7.51
min_lat <- min(as.numeric(DB_raw$glotto_lat), na.rm = TRUE) # -16.77
max_lng <- max(as.numeric(DB_raw$glotto_lon), na.rm = TRUE) # -37.02
min_lng <- min(as.numeric(DB_raw$glotto_lon), na.rm = TRUE) # -78.34

# aggregate rows with shared coordinates
DB <- aggregate(. ~ glotto_lat + glotto_lon, DB_raw, paste, collapse = "; ")

DB <- DB[1:25,] # to be removed after testing

DB_popup <- paste0("<div style='min-width:200px; font-size:13px;'>",
                   "<strong>Indigenous language(s):</strong> ", ifelse(DB$tribe_language != "", DB$tribe_language, "N/A"), "<br>",
                    "<details style='margin-top:5px;'>", "<summary style='cursor:pointer; color:#007bff;'>See more</summary>",
                    # "<strong>Country:</strong> ", ifelse(DB$country != "", DB$country, ""), "<br>",
                    "<strong>Species:</strong> <em>", DB$species_resolved, "</em><br>",
                    "<strong>POWO:</strong> ", # DB$powo_link,
                    "<br>",
                    "<strong>Plant service(s):</strong> ", DB$Plant_service_resolved, "<br>",
                    "<strong>Indigenous group:</strong> ", ifelse(DB$tribe_resolved != "", DB$tribe_resolved, "N/A"), "<br>",
                    # "<strong>Indigenous group / language:</strong> ", ifelse(DB$tribe_resolved != "", DB$tribe_resolved, "N/A"), ifelse(DB$tribe_language != "", paste0(" / ", DB$tribe_language), "N/A"), "<br>",
                    # "<strong>Use:</strong> ", DB$use_category_resolved, ", ", DB$use_subcategory_resolved,
                    "<strong>Source(s):</strong> ", # DB$DOI,
                    "<br>",
                    "<strong>Reference(s):</strong> ", DB$reference,
                    # "<br>",
                    "</div>")
```

```{r map}
# map setup
DBmap <- leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
  addTiles() %>%  # add default OpenStreetMap map tiles
  setView(lat = initial_lat, lng = initial_lng, zoom = initial_zm) %>%
  setMaxBounds(
    lng1 = min_lng, lat1 = min_lat, # southwest corner
    lng2 = max_lng,  lat2 = max_lat # northeast corner
  ) %>%
  addMarkers(lng=as.numeric(DB$glotto_lon), lat=as.numeric(DB$glotto_lat),
             popup=DB_popup
             ) %>%
  addEasyButton(easyButton(
    icon = "fa-search-plus", title = "Zoom in",
    onClick = JS("function(btn, map){ map.zoomIn(); }")
    )
  ) %>%
  addEasyButton(easyButton(
    icon="fa-home", title="Reset view",
    onClick = JS(sprintf("function(btn, map){ map.setView([%s, %s], %s); }", initial_lat, initial_lng, initial_zm))
    )
  ) %>%
  # addEasyButton(easyButton(
  #   icon="fa-crosshairs", title="Locate me",
  #   onClick=JS("function(btn, map){ map.locate({setView: true}); }")
  #   )
  # ) %>%
  addEasyButton(
    easyButton(icon = "fa-download", title = "Download data",
      onClick = JS("
        function(btn, map) {
          var link = document.createElement('a');
          link.href = 'camara_powo_vpa_new_rclverified_website.csv';
          link.download = 'useful-plants-of-amazonia.csv';
          document.body.appendChild(link);
          link.click();
          document.body.removeChild(link);
        }")
      )
    )

# print map
DBmap
```

Filter Data {data-navmenu="Database Maps"}
===================================== 
<!-- {data-orientation=rows}  --> <!-- Row {data-height=100} -->
-----------------------------------------------------------------------
###

```{r interactive map filters}
DB_raw <- DB_raw[1:50,] # to be removed after testing

# UI filters
# fluidRow(
#   column(12,
tags$div(
  style = "display: flex; gap: 10px; align-items: center; padding: 5px; border-radius: 8px; flex-wrap: wrap;", # background-color: #f8f9fa; box-shadow: 0 1px 3px rgba(0,0,0,0.1)
  div(
    style = "flex: 1;",
    pickerInput("species", "Species",
                choices = unique(DB_raw$species_resolved),
                selected = unique(DB_raw$species_resolved),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 1;",
    pickerInput("use", "Use",
                choices = unique(DB_raw$use_category_resolved),
                selected = unique(DB_raw$use_category_resolved),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 1;",
    pickerInput("part", "Plant part",
                choices = unique(DB_raw$plant_part_resolved),
                selected = unique(DB_raw$plant_part_resolved),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
    style = "flex: 1;",
    pickerInput("language", "Language",
                choices = unique(DB_raw$tribe_language),
                selected = unique(DB_raw$tribe_language),
                multiple = TRUE,
                options = list(
                  `actions-box` = TRUE,
                  `live-search` = TRUE
                  ))),
  div(
  style = "flex: 0; margin-top: 12px;",
  downloadButton("downloadData", "Data"))
)
# ))
```

<!-- Row {data-height=900} -->
<!-- ----------------------------------------------------------------------- -->
<!-- ### -->

```{r interactive map output}
# interactive map output
# prev leafletOutput("mymap", height = 500)
div(
  style = "width: 100%; height: 650px; position: relative; margin-top: 10px;",
  leafletOutput("mymap", height = "100%")
)

# reactive data filtering
filtered_data <- reactive({
  # req(input$species, input$part, input$use, input$language)
  DB_raw %>%
    filter(
      species_resolved %in% input$species,
      use_category_resolved %in% input$use,
      plant_part_resolved %in% input$part,
      tribe_language %in% input$language
    )
})

# initial map render
output$mymap <- renderLeaflet({
  leaflet(options = leafletOptions(zoomControl = FALSE)) %>%
    addTiles() %>%
    setView(lat = initial_lat, lng = initial_lng, zoom = initial_zm) %>%
    setMaxBounds(
      lng1 = min_lng, lat1 = min_lat, # southwest corner
      lng2 = max_lng,  lat2 = max_lat # northeast corner
    ) %>%
  addEasyButton(easyButton(
    icon = "fa-search-plus", title = "Zoom in",
    onClick = JS("function(btn, map){ map.zoomIn(); }")
    )
  ) %>%
  addEasyButton(easyButton(
    icon="fa-home", title="Reset view",
    onClick = JS(sprintf("function(btn, map){ map.setView([%s, %s], %s); }", initial_lat, initial_lng, initial_zm))
    )
  )
})

# update map markers dynamically
observe({
  leafletProxy("mymap", data = filtered_data()) %>%
    clearMarkers() %>%
    addMarkers(~as.numeric(glotto_lon), ~as.numeric(glotto_lat), popup = ~reference)
})

# dynamic download button
output$downloadData <- downloadHandler(
  filename = function() {
    paste("useful-plants-of-amazonia-filtered-", Sys.Date(), ".csv", sep = "")
  },
  content = function(file) {
    write.csv(filtered_data(), file, row.names = FALSE)
  }
)
```

Home
===================================== 
Column {.tabset}
-----------------------------------------------------------------------
### ABOUT (`r Sys.Date()`)

The Useful Plants of Amazonia project is developed at Rodrigo Cámara-Leret's lab (https://rcamaraleret.com/), a research group focused on the conservation of biological and cultural heritage. It is supported by a XX grant. This website () was developed by Nisha Marwaha (https://github.com/nmarwaha).

RESOURCES

XX paper citation</br>
XX database citation</br>
XX github link

CONTACT INFORMATION

Rodrigo Cámara-Leret</br>
Department of Systematic and Evolutionary Botany</br>
University of Zurich</br>
Zollikerstrasse 107, 8008 Zurich</br>
Switzerland</br>
Phone: +41 (0)44 634 84 11</br>
e-mail: rodrigo.camaraleret@uzh.ch

```{r}

```

### README

ABOUT DATA DOWNLOADS

- You can use this dataset freely and share it with your collaborators.

- The data have been compiled either from the literature or our own fieldwork or that from our collaborators. In some cases we requested data to the authors, while in others data were incorporated from the original publications.

- Useful Plants of Amazonia () is not the author/owner of the data. It is only a way of sharing them with the scientific community. If you decide to use this dataset in your projects, you must mention this web service: "This work has used the Useful Plants of Amazonia database ()". This does not preclude citing the author of individual studies when needed. You will find the references located in the xx file.

- Use this dataset under your own risk. We are not responsible for the accuracy of the results derived from your research.

- If you have any problems downloading the data, please let us know.

HOW TO CONTRIBUTE

- If you have a study that you think could be included in the database, please send us an e-mail, and we'll send you the necessary information. Also we would be happy to know about potential mistakes you spot.

```{r}

```

